Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 content/appendix.tex
restating lemma
remove finished todos
sorting citations; adding efficiency lemma and proof
reformulating proof

@@

\otodo{restate the lemma before the proof}

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
  By definition of $\backCC$,
  \begin{align*}
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    &=\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)=\ell,\,\forall r\,.\,\ell(r)\ne\top_T\}\\
    &=\{d\,|\,\forall r\in R,\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\}.
  \end{align*}

>>>>

\efficient*
\begin{proof}
\leavevmode
  \begin{enumerate}
    \item The identity function is represented as $\lambda r\,.\,\setpair{\bot_T}{\top_T}$. 
    The top function is represented as $\lambda r\,.\,\setpair{\top_T}{\top_T}$.
    \item Lemmas~\ref{lem:equalComp} and \ref{lem:equalMeet} show that the representation of micro functions is closed under composition and meet.
    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice. Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice. $\rcc$ is a finite set. Hence, the mapping
    \[
      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
    \]        
    also forms a finite-height lattice \cite{nielson1999principles}.

    Furthermore, $\lcc_\rcc$ is a finite set. 
    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types. There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
    \[
      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
    \]
    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
    \item All operations can be computed in $O(\rcc\times T)$ time. Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
    \item The space bound is $O(\rcc\times T)$.\qedhere
  \end{enumerate}
\end{proof}

@@

%\otodo{restate the lemma before the proof}
\onlycorrrec*
\begin{proof}[\textbf{Proof of Lemma~\ref{lem:onlycorrrec}}]
  By definition of $\backCC$,
  \begin{align*}
    \backCC(\resultIDE\left(\transCC_R(P)\right))
    &=\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)=\ell,\,\forall r\,.\,\ell(r)\ne\top_T\}\\
    &=\{d\,|\,\forall r\in R,\,\resultIDE(\transCC_R(P))(n)(d)(r)\ne\top_T\}.
  \end{align*}
